Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
move framework stuff to the framework section

\subsection{Correctness Proof of Surely \lazyD\ Cast Representations}
\label{secc:framework:correctness}

@@

In this section we prove \lazyD\ hypercoercions is correct by showing it, as a 
cast representation, is surely \lazyD\ and a monoid. To use hypercoercion as a 
cast representation in our framework, we need to defined four functions: $ 
cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and $ applyCast(c,v) $. We have defined 
the first three functions in Section~\ref{sec:hypercoercion-definition}. Now we 
define the $ applyCast(c,v) $

\todo[inline]{``monoidic'' is not a word. -JS}

We use bisimulation to proof equivalence between the two machines.
\todo[inline]{Which two machines? -JS}

\subsection{\lazyD\ Hyper-coercion Respect \ineffCEKD}
\label{sec:LDHC-correct}

\figref{hc-applyCast} defines $ applyCast $, the last interface function.
We generalize shallow-consistency to middles and values ($ m \smile v $) in the 
natural way.
Applying the identity cast for the 
dynamic type succeeds immediately. When applying a compound cast, we firstly 
apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
is the failure.
$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.

\begin{theorem}[\lazyD{} hypercoercion Respect $ \mathcal{C}_\mathtt{D} $]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
	Lemma~\ref{thm:hc-surely-lazyD}, and 
	Proposition~\ref{thm:hc-monoid}.
\end{proof}

\subsection{Extra Theorems}

In these section we show some extra theorems that might be useful in proving 
the correctness of other cast representations.

@@

>>>>

\subsection{Surely \lazyD\ Cast Representations Respect \ineffCEKD}
\label{secc:framework:correctness}

@@

@@

In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
correct.

To use hypercoercion as a 
cast representation in our framework, we need to defined four functions: $ 
cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and $ applyCast(c,v) $. We have defined 
the first three functions in Section~\ref{sec:hypercoercion-definition}. Now we 
define the $ applyCast(c,v) $  in \figref{hc-applyCast}

Applying the identity cast for the 
dynamic type succeeds immediately. When applying a compound cast, we firstly 
apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
is the failure.
$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
In the definition of $ applyMiddle(\ell,m,v) $, we generalize 
shallow-consistency to compare middles and values ($ m \smile v $) in the 
natural way.

\begin{theorem}[\lazyD{} hypercoercion Respect \ineffCEKD]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
	Lemma~\ref{thm:hc-surely-lazyD}, and 
	Proposition~\ref{thm:hc-monoid}.
\end{proof}
